pdp: An R Package for Constructing Partial Dependence Plots

### 2017-01-02 manuscript/greenwell.tex
minor edits

Currently supported models are described in Table~\ref{tab:models}. In a lot of these cases, \code{partial} should be able to automatically determine appropriate values for the options \code{type} (i.e., \code{"regression"} or \code{"classification"}) and \code{train}\footnote{For reasons described in the package documentation, it is good practice to always supply the training data via the \code{train} argument in the call to \code{partial}; see \code{?partial for details}} (the original training data). In other situations, the user may need to specify one or both of these additional arguments. These two arguments allow \code{partial} to be flexible enough to handle many of the model types not listed in Table~\ref{tab:models}; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} and projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package.

>>>>

Currently supported models are described in Table~\ref{tab:models}. In these cases, \code{partial} should be able to automatically determine an appropriate value for \code{type} (\code{"regression"} or \code{"classification"}). In other situations, the user may need to specify this argument. This allows \code{partial} to be flexible enough to handle many of the model types not listed in Table~\ref{tab:models}; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} and projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package.

If \code{train = NULL}, \code{partial} tries to extract the original training data from the fitted model object. For objects that typically store a copy of the training data (e.g., objects of class \code{"BinaryTree"}, \code{"RandomForest"}, and \code{"train"}), this is straightforward. Otherwise, \code{partial} will attempt to extract the call stored in \code{object} (if available) and use that to evaluate the training data in the same environment from which \code{partial} was called. This can cause problems when, for example, the training data have been changed after fitting the model, but before calling \code{partial}. Hence, it is good practice to always supply the training data via the \code{train} argument in the call to \code{partial}\footnote{For brevity, we ignore this option in most of the examples in this paper.}.
